---
title: "P8105 Homework 1"
author: "Yuelin Long  yl3181"
date: "September 14, 2018"
output: github_document
---

#Problem 1
Create and take the column means of a data frame comprised of:

+ A random sample of size 10 from a uniform[0, 5] distribution
+ A logical vector indicating whether elements of the sample are greater than 2
+ A (length-10) character vector
+ A (length-10) factor vector

```{r warning=FALSE}
library(tidyverse)

set.seed(1)
first_data = tibble(
random_sample = runif(10,0,5),
logic_random_sample = random_sample > 2,
char_vec = unlist(strsplit("mynameisYL","")),
fac_char_vec = factor(char_vec)
)

sapply(first_data,mean)
```


```{r eval=FALSE}
num_logic_random_sample = as.numeric(logic_random_sample)
num_char_vec = as.numeric(char_vec)
num_fac_char_vec = as.numeric(fac_char_vec)
```
For format changes, as.numeric() works for logical vectors and factor vectors, but won't work for character vector.

```{r eval=FALSE}
mult_change_char_vec = as.numeric(as.factor(char_vec))
mult_change_fac_char_vec = as.numeric(as.character(fac_char_vec))
```
For multiple format changes, if a vector has been converted to factor(numeric) before, all types vectors can be changed to numeric.


#Problem 2
Create a data frame comprised of:

+ x: a random sample of size 1000 from a standard Normal distribution
+ y: a random sample of size 1000 from a standard Normal distribution
+ A logical vector indicating whether the x + y > 0
+ A numeric vector created by coercing the above logical vector
+ A factor vector created by coercing the above logical vector

```{r}
set.seed(1)
x = rnorm(1000)

set.seed(2)
y = rnorm(1000)

logi_xy = (x + y > 0)
num_logi_xy = as.numeric(logi_xy)
fac_num_logi = as.factor(num_logi_xy)

second_data = tibble(x, y , logi_xy , num_logi_xy , fac_num_logi)
```
Dataframe Description:

* Size of the dataset is: `r dim(second_data)`
* x statistics: Mean of x is `r mean(x)`, while median of x is `r median(x)`
* The proportion of "true" cases in logical vector is `r sum(num_logi_xy)/length(num_logi_xy)`

```{r}
library(ggplot2)
ggplot(second_data, aes(x = x, y = y, color = logi_xy)) + geom_point() + labs(color = "numeric variables")  
ggsave("x-y scatter plot with logi color.png")

ggplot(second_data, aes(x = x, y = y, color = num_logi_xy)) + geom_point() + labs(color = "numeric variables")  
ggplot(second_data, aes(x = x, y = y, color = fac_num_logi)) + geom_point() + labs(color = "factor variables") 
```
