---
title: "p8105_hw1_yl3181"
author: "Yuelin Long"
date: "September 14, 2018"
output: html_document
---

#Problem 1
Create and take the column means of a data frame comprised of:

+ A random sample of size 10 from a uniform[0, 5] distribution
+ A logical vector indicating whether elements of the sample are greater than 2
+ A (length-10) character vector
+ A (length-10) factor vector

```{r warning=FALSE}
set.seed(1)
random_sample = runif(10,0,5)
logic_random_sample = random_sample > 2
char_vec = unlist(strsplit("mynameisYL",""))
fac_char_vec = factor(char_vec, labels = c(1:9))

first_data = cbind(random_sample,logic_random_sample,char_vec,fac_char_vec)
mean_first_data = colMeans(apply(first_data,2,as.numeric))
print(mean_first_data)
```


```{r eval=FALSE}
num_logic_random_sample = as.numeric(logic_random_sample)
num_char_vec = as.numeric(char_vec)
num_fac_char_vec = as.numeric(fac_char_vec)
```
For format changes, as.numeric() works for logical vectors and factor vectors, but won't work for character vector.

```{r eval=FALSE}
mult_change_char_vec = as.numeric(as.factor(char_vec))
mult_change_fac_char_vec = as.numeric(as.character(fac_char_vec))
```
For multiple format changes, if a vector has been converted to factor(numeric) before, all types vectors can be changed to numeric.

Note: In my dataframe, factor vector is numeric. If use character factor vector, it won't be converted to numeric.
